### 2022-06-23 Report/manuscript.tex
Updating readme,report,codes and lists

@@

@@

>>>>

    \subsection*{Run Time Perfomance of Sequential Kronecker Products}

    \begin{figure}[ht!]
        \centering 
        \includegraphics[width=0.75\linewidth]{figs/hw0a1.png} \par 
        \caption{Monter Carlo Experiment with 5000.}
        \label{fig:hw0a1} 
    \end{figure}

    \begin{figure}[ht!]
        \centering 
        \includegraphics[width=0.75\linewidth]{figs/hw0a2.png} \par 
        \caption{Monter Carlo Experiment with 10000 runs.}
        \label{fig:hw0a2} 
    \end{figure}

    \subsection*{Show that $\text{eig}(\boldsymbol{A} \otimes \boldsymbol{B}) = \text{eig}(\boldsymbol{A}) \otimes \text{eig}(\boldsymbol{B})$}

@@

    \subsection*{Run Time Perfomance of Hadamard Product}

    \begin{figure}[ht!]
        \centering 
        \includegraphics[width=0.75\linewidth]{figs/hw1a1.png} \par 
        \caption{Monter Carlo Experiment with 1000 runs.}
        \label{fig:hw1a1} 
    \end{figure}

    \subsection*{Run Time Perfomance of Kronecker Product}

    \begin{figure}[ht!]
        \centering 
        \includegraphics[width=0.75\linewidth]{figs/hw1a2.png} \par 
        \caption{Monter Carlo Experiment with 1000 runs.}
        \label{fig:hw1a2} 
    \end{figure}

    \subsection*{Run Time Perfomance of Khatri-Rao Product}

    \begin{figure}[ht!]
        \centering 
        \includegraphics[width=0.75\linewidth]{figs/hw1a3.png} \par 
        \caption{Monter Carlo Experiment with 1000 runs.}
        \label{fig:hw1a3} 
    \end{figure}

@@

    \subsection*{Run Time Performance of Khatri-Rao Product for Different Implementations}

    \begin{figure}[ht!]
        \centering 
        \includegraphics[width=0.75\linewidth]{figs/hw2a1.png} \par 
        \caption{Monter Carlo Experiment with 250 runs and R = 2.}
        \label{fig:hw2a1} 
    \end{figure}

    \begin{figure}[ht!]
        \centering 
        \includegraphics[width=0.75\linewidth]{figs/hw2a2.png} \par 
        \caption{Monter Carlo Experiment with 250 runs and R = 4.}
        \label{fig:hw2a2} 
    \end{figure}

    \subsection*{Run Time Perfomance of Sequential Khatri-Rao Products}

    \begin{figure}[ht!]
        \centering 
        \includegraphics[width=0.75\linewidth]{figs/hw2a3.png} \par 
        \caption{Monter Carlo Experiment with 250 runs.}
        \label{fig:hw2a3} 
    \end{figure}
